Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions

### 2022-11-25 manuscript.Rmd
Minor corrections

abstract: |
  Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

@@

In recent years different concerns on credibility of  empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

>>>>

abstract: |
  Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns about the credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in the first stage 52 showed a discrepancy larger than 5% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

@@

In recent years different concerns on the credibility of  empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

### 2022-11-25 manuscript.tex
Minor corrections

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns on credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc) or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in a first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as: reporting inconsistencies, lack of some data or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

@@

In recent years different concerns on credibility of empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al. (2020); Errington et al. (2021); Open Science Collaboration (2015)). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

>>>>

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, however, this relevance relies on its credibility. In recent years different concerns about the credibility of psychological research have emerged. Analytical reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the analytical reproducibility and data reusability of a set of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in psychology used in a previous study, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or on request. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 meta-analyses from different sources. Of these, in the first stage 52 showed a discrepancy larger than 5\% in the main results, in 25 of them, this discrepancy was solved with minor adjustments, or correction of coding errors. In the remaining 27, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of some data, or transcription errors. Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. On the other hand, the implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

@@

In recent years different concerns on the credibility of empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., Artner et al. (2020); Errington et al. (2021); Open Science Collaboration (2015)). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.
